Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-05 writeup/gz_hubble_data.tex

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
\caption{Surface brightness vs. redshift of 118,083 galaxies in the ACS sample. The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}
\label{fig:sb_redshift}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
\caption{Surface brightness vs. redshift of 3,950 \ferengi{} images and the 102,548 galaxies in the ACS sample which had measured values of $\mu$ and $z$. The color histogram counts the number of \ferengi{} images as a function of $\mu$ and $z_{\rm simulated}$. The white contours show counts for the ACS sample as a function of $\mu$ and $z$, with contours starting at N = 1000 and separated by 1000 up to 7000.} 
\label{fig:sb_redshift}
\end{center}
\end{figure}
